---
title: "18233038_WatanabeMotohiro_PS2"
author: "18233038_WatanabeMotohiro"
date: "`r Sys.Date()`"
output: html_document
---

### preparation

```{r}
library(rethinking)
data(foxes)
df <- foxes
```

### 5H1

```{r}
m1 <- map(
  alist(
    weight ~ dnorm( mu , sigma ) ,
    mu <- a + b_area*area ,
    a ~ dnorm(0,100),
    b_area ~ dnorm(0,10),
    sigma ~ dunif(0,50)
  ) , data=df )

m2 <- map(
  alist(
    weight ~ dnorm( mu , sigma ) ,
    mu <- a + b_group*groupsize ,
    a ~ dnorm(0,100),
    b_group ~ dnorm(0,10),
    sigma ~ dunif(0,50)
  ) , data=df )

precis(m1)
precis(m2)
```

(fig.1)area&weight

```{r}
x.seq <- seq(from=0,to=6,by=0.025)
mu <- link( m1 , data=list(area=x.seq) )
mu.mean <- apply( mu , 2 , mean )
mu.ci <- apply( mu , 2 , PI )
plot( weight ~ area , data=df , col="blue" )
lines( x.seq , mu.mean )
lines( x.seq , mu.ci[1,] , lty=2 )
lines( x.seq , mu.ci[2,] , lty=2 )
```

(fig.2)groupsize&weight

```{r}
x.seq <- seq(from=1,to=9,by=0.5)
mu <- link( m2 , data=list(groupsize=x.seq) )
mu.mean <- apply( mu , 2 , mean )
mu.ci <- apply( mu , 2 , PI )
plot( weight ~ groupsize , data=df , col="red" )
lines( x.seq , mu.mean )
lines( x.seq , mu.ci[1,] , lty=2 )
lines( x.seq , mu.ci[2,] , lty=2 )
```

Groupsize is more important for predicting fox body weight than area.

### 5H2

```{r}
m3 <- map(
  alist(
    weight ~ dnorm( mu , sigma ) ,
    mu <- a + b_area*area + b_group*groupsize ,
    a ~ dnorm(0,100),
    c(b_area,b_group) ~ dnorm(0,10),
    sigma ~ dunif(0,50)
  ) , data=df )
precis(m3)
```

(fig.3)groupsize fixed

```{r}
area.seq <- seq(from=1,to=6,by=0.5)
pred.dat <- data.frame( area=area.seq , groupsize=mean(df$groupsize) )
mu <- link( m3 , data=pred.dat )
mu.mean <- apply( mu , 2 , mean )
mu.ci <- apply( mu , 2 , PI )
plot( weight ~ area , data=df , type="n" )
lines( area.seq , mu.mean )
lines( area.seq , mu.ci[1,] , lty=2 )
lines( area.seq , mu.ci[2,] , lty=2 )
```

(fig.4)area fixed

```{r}
gs.seq <- seq(from=1,to=9,by=0.5)
pred.dat <- data.frame( area=mean(df$area) , groupsize=gs.seq )
mu <- link( m3 , data=pred.dat )
mu.mean <- apply( mu , 2 , mean )
mu.ci <- apply( mu , 2 , PI )
plot( weight ~ groupsize , data=df , type="n" )
lines( gs.seq , mu.mean )
lines( gs.seq , mu.ci[1,] , lty=2 )
lines( gs.seq , mu.ci[2,] , lty=2 )
```

Importance of area appeared because of collinearity with groupsize. And, importance of groupsize still is clear.

### 5H3

```{r}
m4 <- map(
  alist(
    weight ~ dnorm( mu , sigma ) ,
    mu <- a + b_food*avgfood + b_group*groupsize ,
    a ~ dnorm(0,100),
    c(b_food,b_group) ~ dnorm(0,10),
    sigma ~ dunif(0,50)
) , data=df )

m5 <- map(
  alist(
    weight ~ dnorm( mu , sigma ) ,
    mu <- a + b_food*avgfood + b_group*groupsize + b_area*area ,
    a ~ dnorm(0,100),
    c(b_food,b_group,b_area) ~ dnorm(0,10),
    sigma ~ dunif(0,50)
  ) , data=df )
```

(a)

```{r}
precis(m4)
```

Putting avgfood into model is favorable because coefficients of avgfood is estimated higher than area.

(b)

```{r}
precis(m5)
```

This model may has multicollinearity problem because vast area can be thought to have much food. So, result of m5 may be biased.
